---
title: "capstone_doc"
author: "Marisa Guarinello"
date: "April 28, 2015"
output: html_document
-----

```{r,global_knitr_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, fig.path="../figures/")
#Here are global options to echo=false for all code chunks and where to save figures. 
```

```{r, load_libraries, echo=FALSE, results="hide", message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
#For load_libraries, the code and results will be hidden and if the code chunk gives a message or warning it will not be shown in the html.
```

#Gapminder Report for New Zealand, India, Italy

This report will provide some information about life expectancy and GDP per capita for New Zealand, India, and Italy using the gapminder dataset.

```{r, load_data}
gapminder <- read.csv("../data/gapminder.csv")
```

```{r, filter_3}
gm_3 <- gapminder %>%
  filter(country %in% (c("New Zealand","India","Italy")))
```

Here are the first 6 lines of the data set.
```{r,head_gm_3}
head(gm_3)
```

This dataset for these 3 countries has `r nrow(gm_3)` rows and `r ncol(gm_3)` columns.

Here are plots showing GDP per capita over time for each of the 3 countries
```{r,plot}
ggplot(gm_3,aes(y=gdpPercap, x=year, color=year))+
  geom_point(size=4)+
  scale_x_log10()+
  facet_wrap(~ country)
```

Let's look at the same data on one plot
```{r,plot2}
ggplot(gm_3,aes(y=gdpPercap, x=year, color=country))+
  geom_point(size=4, aes(group=country)) +
  scale_x_log10()
```

From these results I observe that, while both the GDPs for Italy and New Zealand (*first world countries*) increase over time, the rate of increase has been steadily increasing for Italy while that of New Zealand dipped down sharply in the mid-1990s (approximately) before continuing to increase at a similar rate to Italy, though lower value. India (*third world country*) has a far lower GDP per capita than India or Italy; perhaps a result of a very large population. What do you think?
